timesliced_random_cell_selection

### 2018-11-26 src/biological_data_prep.Rmd
kelvin to celsius conversions on both datasets

# Package dependencies
You can load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). 
Note this function checks to see if the packages are installed first.
Th
```{r pre-install packages, message=FALSE}
packages <- c("packrat", "rworldmap", "dplyr","plyr", "rgdal", "sp", "raster", "tibble", "useful", "marmap")
source("../src/ipak.R")
ipak(packages)
suppressMessages(ipak)
```

@@

>>>>

# Package dependencies
You can load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). 
Note this function checks to see if the packages are installed first.

```{r pre-install packages, message=FALSE}
packages <- c("packrat", "rworldmap", "dplyr","plyr", "rgdal", "sp", "raster", "tibble", "useful", "marmap", "weathermetrics")
source("../src/ipak.R")
ipak(packages)
suppressMessages(ipak)
```

@@

# add a col for temp variable in celsius (every-day person readable)

```{r}
data_aea$temp_celsius_depth <- kelvin.to.celsius(data_aea$temp_depth, round = 4) # 4 is the number of decimal places. the values are expressed to 4
data_aea$temp_celsius_surface <- kelvin.to.celsius(data_aea$temp_surface, round = 4)
write.csv(data_aea, "../output/bio/data_aea_cell_amo_nao_bins_env_depth_cellobno_env_naocor_cels.csv", row.names = FALSE)
```

### 2018-11-26 src/timesliced_random_cell_selection.Rmd
kelvin to celsius conversions on both datasets

```{r pre-install & load packages, include=FALSE}
install.packages("pacman")
library(pacman)
p_load(raster, dplyr, data.table, sp, adehabitatHR, rgdal, rworldmap, ncdf4, marmap, plyr)
```

@@

>>>>

```{r pre-install & load packages, include=FALSE}
if (!require("pacman")) install.packages("pacman")
p_load(raster, dplyr, data.table, sp, adehabitatHR, rgdal, rworldmap, ncdf4, marmap, plyr, weathermetrics)
```

@@

# add a col for temp variable in celsius (every-day person readable)

Uses the weathermetrics package

```{r}
background_all$temp_celsius_depth <- kelvin.to.celsius(background_all$temp_depth, round = 4) # 4 is the number of decimal places. the values are expressed to 4
background_all$temp_celsius_surface <- kelvin.to.celsius(background_all$temp_surface, round = 4)
write.csv(background_all, "../output/bio/background_complete_obs_cels.csv", row.names = FALSE)
```
